When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-03-14 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
removed comment
typo

To determine the influence of task performance on the association of SVs and $n$-back level, we performed MLM. 
We applied restricted maximum likelihood (REML) to fit the model.
As an effect size measure for random effects we first calculated the intraclass correlation (ICC), which displays the proportion of variance that is explained by differences between persons.
Second, we estimated a random slopes model of $n$-back level (level 1, fixed, and random factor: 0-back, 1-back, 2-back, 3-back) predicting SV nested within subjects.
As Mussel et al.[-@Mussel2016] could show, participants with high versus low NFC not only have a more shallow decline in performance with higher $n$-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.
We controlled for performance, i.e., $d'$ (level 1, fixed factor, continuous), median RT (level 1, fixed factor, continuous) in order to eliminate a possible influence of declining performance on SV ratings.
$$
SV \sim level\ + d' + median RT + (level|subject)
$$
Level-1-predictors were centered within cluster as recommended by Enders & Tofighi[-@Enders2007]. 
By this, the model yields interpretable parameter estimates. 
If necessary, we will adjusted the optimization algorithm to improve model fit. 
We visually inspected the residuals of the model for evidence to perform model criticism. 
This was done by excluding all data points with absolute standardized residuals above 3 SD. 
As effect size measures, we calculated pseudo $R^{2}$ for our model and $f^{2}$ to estimate the effect of $n$-back level according to Lorah[-@Lorah2018].

@@

Despite the visual separation of the SVs of participants with very low and high NFC scores in higher $n$-back levels, the NFC group did not reach significance in predicting SVs.
This was likely due to the bandwidth of SVs of participants with NFC scores around the median, and due to the fact that the difference appeared most pronounced for 4-back, and we only analyzed the difference scores between 1- and 2-back and 2- and 3-back.
As the exploratory analysis showed, only 4-back yielded a significant group difference, and SVs of participants with NFC scores above the median were higher for 2- to 4-back and lower for 1-back.
The analysis of NASA-TLX scores showed that the sum score increased with every $n$-back level, and that participants with NFC scores below the median had higher NASA-TLX scores for 3- and 4-back than those below the median.
This demonstrates that higher $n$-back levels have a higher discriminatory power regarding inter-individual differences in subjective effort perception.
This was also supported by the fact that higher $n$-back levels were perceived as more aversive, and participants with NFC scores below the median reported higher aversion than those with NFC scores above the median.
<!-- CK: für die Diskussion wäre es noch gut, eine Entscheidung zu treffen, ob die jeweilige Hypothese angenommen oder abgelehnt wurde und das klar hinzuschreiben. -->

>>>>

To determine the influence of task performance on the association of SVs and $n$-back level, we performed MLM. 
We applied restricted maximum likelihood (REML) to fit the model.
As an effect size measure for random effects we first calculated the intraclass correlation (ICC), which displays the proportion of variance that is explained by differences between persons.
Second, we estimated a random slopes model of $n$-back level (level 1, fixed, and random factor: 0-back, 1-back, 2-back, 3-back) predicting SV nested within subjects.
As Mussel et al.[-@Mussel2016] could show, participants with high versus low NFC not only have a more shallow decline in performance with higher $n$-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.
We controlled for performance, i.e., $d'$ (level 1, fixed factor, continuous), median RT (level 1, fixed factor, continuous) in order to eliminate a possible influence of declining performance on SV ratings.
$$
SV \sim level\ + d' + median RT + (level|subject)
$$
Level-1-predictors were centered within cluster as recommended by Enders & Tofighi[-@Enders2007]. 
By this, the model yields interpretable parameter estimates. 
If necessary, we adjusted the optimization algorithm to improve model fit. 
We visually inspected the residuals of the model for evidence to perform model criticism. 
This was done by excluding all data points with absolute standardized residuals above 3 SD. 
As effect size measures, we calculated pseudo $R^{2}$ for our model and $f^{2}$ to estimate the effect of $n$-back level according to Lorah[-@Lorah2018].

@@

Despite the visual separation of the SVs of participants with very low and high NFC scores in higher $n$-back levels, the NFC group did not reach significance in predicting SVs.
This was likely due to the bandwidth of SVs of participants with NFC scores around the median, and due to the fact that the difference appeared most pronounced for 4-back, and we only analyzed the difference scores between 1- and 2-back and 2- and 3-back.
As the exploratory analysis showed, only 4-back yielded a significant group difference, and SVs of participants with NFC scores above the median were higher for 2- to 4-back and lower for 1-back.
The analysis of NASA-TLX scores showed that the sum score increased with every $n$-back level, and that participants with NFC scores below the median had higher NASA-TLX scores for 3- and 4-back than those below the median.
This demonstrates that higher $n$-back levels have a higher discriminatory power regarding inter-individual differences in subjective effort perception.
This was also supported by the fact that higher $n$-back levels were perceived as more aversive, and participants with NFC scores below the median reported higher aversion than those with NFC scores above the median.
